---
title: "Automated scoring using ANNs - detailed methodology"
output: html_notebook
---

This R notebook is intended to detail the methodology used to create and run the ANN scoring.

## System

This project was conducted in R using the Keras machine learning package with Tensorflow back end. 
Keras is a machine learning application progamming interface (API) that provides a simplified library of machine
learning functions which can be connected to a machine learning engine in order to run machine learning models. 
Tensorflow is Google's open source machine learning engine, and is the default engine, or "back-end" for Keras. 
Keras and Tensorflow can be installed in R using the following code.


```{r}
install.packages("pacman")
library(pacman)
p_load(tensorflow)
install_github("rstudio/keras")
library(keras)

#note Keras has some python dependencies and may require require python and conda to be installed. 
#See System&Installation.R for more detailed instructions.

```

## Data preparation



```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
